---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Mapping the Evidence Gaps on Modifiable Risk Factors for Stroke in Middle and Low Income Countries (ATLAS Stroke Project)

<!-- badges: start -->
<!-- badges: end -->

This repository is a [`docker`](https://www.docker.com/get-started)-containerised, [`{targets}`](https://docs.ropensci.org/targets/)-based, [`{renv}`](https://rstudio.github.io/renv/articles/renv.html)-enabled [`R`](https://cran.r-project.org/) workflow for the ATLAS Stroke Project. The project aims to map the evidence gaps on modifiable risk factors for stroke in middle and low income countries. This is part of the **A**dvancing **T**hematic Research **L**andscapes **AS**sessment in Global Health (ATLAS) initiative

## About the Project

The burden of stroke is among the top five causes of mortality and morbidity in middle and low income countries, and this burden is growing, yet evidence on contributing causes and the efficacy of interventions appears to be disproportionately generated in high-income countries for discrete population groups. The **ATLAS Stroke** research project aims to map existing evidence on stroke globally and identify gaps in knowledge on modifiable risk factors in middle and low income countries. This research project is part of the **A**dvancing **T**hematic Research **L**andscapes **AS**sessment in Global Health (ATLAS) initiative, a global initiative to map evidence gaps on various health topics and challenges in middle and low income countries.


## Repository Structure

The project repository is structured as follows:

```
altas-stroke
    |-- .github/
    |-- data-raw/
    |-- data/
    |-- outputs/
    |-- R/
    |-- renv/
    |-- reports/
    |-- slides/
    |-- tests/
    |-- .Rprofile
    |-- packages.R
    |-- _targets.R
    |-- renv.lock
```

* `.github` contains project testing and automated deployment of outputs workflows via continuous integration and continuous deployment (CI/CD) using Github Actions.

* `data-raw/` contains raw datasets, usually either downloaded from source or added manually, that are used in the project.

* `data/` contains intermediate and final data outputs produced by the workflow.

* `outputs/` contains compiled reports and figures produced by the workflow.

* `R/` contains functions developed/created specifically for use in this workflow.

* `renv/` contains `renv` package specific files and directories used by the package for maintaining R package dependencies within the project. The directory `renv/library`, is a library that contains all packages currently used by the project. This directory, and all files and sub-directories within it, are all generated and managed by the `renv` package. Users should not change/edit these manually.

* `reports/` contains literate code for R Markdown and/or Quarto reports rendered in the workflow.

* slides/ contains literate code for R Markdown and/or Quarto slides rendered in the workflow.

* tests/ contains test code for testing the workflow’s LLM outputs.

* `.Rprofile` file is a project R profile generated when initiating `renv` for the first time. This file is run automatically every time R is run within this project, and `renv` uses it to configure the R session to use the `renv` project library.

* `packages.R` file lists out all R package dependencies required by the workflow.

* `_targets.R` file defines the steps in the workflow's data ingest, data processing, data analysis, and reporting pipeline.

* `renv.lock` file is the `renv` lockfile which records enough metadata about every package used in this project that it can be re-installed on a new machine. This file is generated by the `renv` package and should not be changed/edited manually.

## Reproducibility

### R version

This project is built using `R 4.6.1`. To manage R versions, it is recommended to use [`rig`](https://github.com/r-lib/rig) - an R installation manager - to be able to install multiple versions of R and switch between them as needed.

### R package dependencies

This project uses the `{renv}` framework to record R package dependencies and versions. Packages and versions used are recorded in `renv.lock` and code used to manage dependencies is in the `renv` directory and other files in the root project directory.

On starting an R session in the working directory of this repository, first run 

```R
renv::restore()
```

to install R package dependencies. This is only done once when the project is being initiated for the first time by a user.

### The workflow

The current workflow has the following steps:

```{r full-workflow, echo = FALSE, results = "asis"}
cat(
  c(
    "```mermaid",
    targets::tar_mermaid(
      targets_only = TRUE, outdated = FALSE, legend = FALSE, color = FALSE
    ),
    "```"
  ),
  sep = "\n"
)
```


